\LARGE \bf \pyRobots, a toolkit for robot executive control

### 2014-08-20 paper.tex
Added minted.sty 2.0alpha to have inline python code

@@

\begin{itemize}
    \item Turns any Python function into a background action with the decorator
        @action.
    \item Robot actions are non-blocking by default: they are instanciated as
        futures (lightweight threads),
    \item Actions can be cancelled at any time via signals (the
        ActionCancelled signal is raised).
    \item Lock specific resources with a simple @lock(...) in front of the
        actions. When starting, actions will wait for resources to be
        available if needed.
    \item Supports compound resources (like WHEELS == LEFTWHEEL +
        RIGHTWHEEL)
    \item Create event with robot.every(<condition>).do(<action>)
    \item Poses are managed explicitely and can easily be
        transformed from one reference frame to another one
        (integrates with ROS TF when available).
    \item Extensive logging support to debug and replay
        experiments.
\end{itemize}

>>>>

\newmintinline[python]{python}{fontsize=\footnotesize}

@@

\begin{itemize}
    \item Turns any Python function into a background action with the decorator
        \python|@action|.
    \item Robot actions are non-blocking by default: they are instanciated as
        futures (lightweight threads),
    \item Actions can be cancelled at any time via signals (the
        \python|ActionCancelled| signal is raised).
    \item Lock specific resources with a simple \python|@lock(...)| in front of the
        actions. When starting, actions will wait for resources to be
        available if needed.
    \item Supports compound resources (like \python|WHEELS == LEFTWHEEL + RIGHTWHEEL|)
    \item Create event with robot.every(<condition>).do(<action>)
    \item Poses are managed explicitely and can easily be
        transformed from one reference frame to another one
        (integrates with ROS TF when available).
    \item Extensive logging support to debug and replay
        experiments.
\end{itemize}
